% Complete recipe example
\begin{recipe}
[% 
    preparationtime = {\unit[1-2]{h}},
    portion = {\portion{6-8}},
]
{Red Braised Meat}
    \ingredients{%
        & Pork/beef/lamb cubes\\
        & Carrots\\
        1 & Cinnamon stick\\
        2 & Star anise\\
        & Sichuan peppercorns\\
        2 & Bay leaves\\
        2cm chunk & Hotpot seasoning\\
        & Sugar\\
        & Oyster sauce\\
        & Soy sauce\\
        & Dark soy sauce\\
    }
    
    \preparation{%
        \step Pre-cook the meat by frying or boiling. If boiled, add the meat into cold water with salt, ginger slices and green onion, heat it slowly until boiling and scoop off the scum
        \step Heat up oil and sugar in a pot until the sugar carmelizes into a deep red.
        \step Tip the meat into the sugar and fry until the meat is well carmelized.
        \step Add dark soy sauce, oyster sauce, soy sauce and mix together.
        \step Pour in boiling water around the edges of the pot to cover the meat. Don't pour the water directly on the meat because it will wash off the colouring.
        \step Add in the cinnamon stick, star anise, bay leaves, hotpot seasoning, and a good amount of salt.
        \step Cover and cook for for 1-2 hours.
        \step In the last 30 minutes, add in the carrots.
    }
    
    \hint{%
        This dish is a stew, there should be plenty of water left when serving, but not so much that it's hard to find food in it.
    }
    
\end{recipe}